%==========================
% RESUME
%==========================

\documentclass[letterpaper,10pt]{article}

%---------------------------
% PACKAGES AND MARGINS
%---------------------------
\usepackage[top=0.5in, bottom=0.5in, left=1in, right=1in]{geometry} % Adjust margins as needed
\usepackage{parskip}                                                % No paragraph indent, extra spacing
\usepackage{hyperref}                                               % For clickable URLs and links
\usepackage{setspace}                                               % For line spacing if needed
\setstretch{1}                                                      % Slight line spacing

%---------------------------
% CUSTOM COMMANDS
%---------------------------
\newcommand{\resheading}[1]{
  \vspace{10pt}
  \textbf{\large #1}
  \vspace{5pt}
  \hrule
  \vspace{5pt}
}

%---------------------------
% DOCUMENT START
%---------------------------
\begin{document}

%==========================
% CONTACT INFO
%==========================
\begin{center}
    {\LARGE \textbf{Ian Heraty}} \\
    Chicago, Illinois, USA \\
    \textbf{Phone}: \href{tel:+1.630.891.0692}{+1.630.891.0692} \quad\textbullet\quad 
    \textbf{Email}: \href{mailto:heratyian@gmail.com}{heratyian@gmail.com} \quad\textbullet\quad
    \textbf{Blog}: \href{http://heratyian.github.io}{heratyian.github.io}
\end{center}

%==========================
% SUMMARY / OBJECTIVE
%==========================
\resheading{Summary}
Relentless tech innovator, founder, and educator with a track record of 
bringing bold ideas to life. Proficient in scaling software solutions across 
web, mobile, and hardware platforms—driven by a first-principles approach 
to problem-solving. Polyglot developer adept at 
managing teams, and unafraid to tackle uncharted technical challenges. 
Seeking impactful missions that require visionary thinking, rapid execution, 
and uncompromising quality.

%==========================
% EDUCATION
%==========================
\resheading{Education}
\textbf{University of Notre Dame} \hfill \textit{2009 -- 2012}\\
Bachelor of Arts (BA)

%==========================
% PROFESSIONAL EXPERIENCE
%==========================
\resheading{Professional Experience}

\textbf{Discovery Partners Institute (University of Illinois)} \hfill \textit{Jan 2023 -- Present}\\
\emph{Software Development Educator, Chicago, IL}\\
\begin{itemize}
  \item Designed and led advanced curriculum for full stack software development, 
        instilling real-world engineering practices and innovation mindsets.
  \item Mentored diverse cohorts of aspiring technologists, focusing on 
        software development fundamentals, rapid prototyping, and problem-solving.
  \item Collaborated with top-tier companies like John Deere, SAP, HCSC, 
        Zebra Technologies, Underwriters Laboratories, United Airlines, and CIBC to 
        match students with roles in software engineering, consulting, project 
        management, sales, quality assurance, and business analysis.
  \item Successfully guided students to exceed expectations at leading companies, 
        resulting in impactful contributions across various roles, demonstrating the 
        program's effectiveness in real-world job placement.
\end{itemize}

\textbf{Big Green Company} \hfill \textit{Sep 2020 -- Present}\\
\emph{Co-Founder, Chicago, IL}\\
\begin{itemize}
    \item Spearheaded \href{https://receipt-ai.com}{receipt-ai.com}, an innovative, 
          AI-driven platform that enables users to effortlessly upload receipts via SMS, 
          email, or web, making the process seamless and accessible.
    \item Leveraged machine learning to digitize and analyze receipts, providing 
          real-time, actionable insights that drive smarter business decisions.
    \item Directed strategy and product development, ensuring continuous iteration and 
          deployment of cutting-edge solutions that are both user-friendly and revenue-generating.
\end{itemize}

\textbf{Nerdery} \hfill \textit{Mar 2017 -- Sep 2020}\\
\emph{Senior Software Engineer, Chicago, IL}\\
\begin{itemize}
  \item Delivered high-impact software solutions across multiple technology stacks to 
        meet diverse client needs in supply chain management, business processes, 
        consumer goods, and more.
  \item Consistently exceeded client expectations, playing a key role in delivering 
        projects that drove business transformation efficiently and on schedule.
  \item Recognized for exceptional performance, logging the most billable hours of 
        any employee in the Chicago office in both 2018 and 2019, reflecting strong 
        commitment and client satisfaction.
\end{itemize}

\textbf{Mi-Jack Products} \hfill \textit{May 2016 -- Mar 2017}\\
\emph{Software Engineer, Homewood, IL}\\
\begin{itemize}
  \item Delivered impactful solutions by developing a mobile app for "power-in-lock" 
        container shipping smart locks, enabling real-time lock status monitoring, 
        configuration, logging, and firmware updates, streamlining operational efficiency 
        for clients.
  \item Designed and implemented an automated testing framework to detect defects in 
        manufactured smart locks, ensuring high-quality standards and minimizing costly 
        errors in production.
  \item Led development efforts for \emph{Mi-Star V2}, collaborating with stakeholders to 
        align engineering goals, define requirements, and integrate innovative solutions 
        that enhanced product functionality and reliability.
\end{itemize}

\textbf{Freelance iOS Developer} \hfill \textit{Jan 2016 -- Mar 2017}\\
\begin{itemize}
  \item Designed, developed, and launched 3 successful iOS apps on the App Store, 
        delivering high-quality user experiences.
  \item Created interactive and engaging games (e.g., \emph{GoChickenGo}, \emph{GingerCat}), 
        focusing on performance, usability, and scalability.
\end{itemize}

%==========================
% ADDITIONAL ROLES
%==========================
\resheading{Additional Roles}
\textbf{imoo} \hfill \textit{Jan 2016 -- Jun 2016}\\
\emph{Software Localization Consultant}\\
\begin{itemize}
  \item Adapted English-language Android/iOS watch apps and firmware to Thai market, 
        ensuring seamless user experiences.
  \item Contributed linguistic and technical expertise to optimize 
        cross-cultural product adoption.
\end{itemize}

\textbf{Nanshan Second Foreign Language School} \hfill \textit{Aug 2012 -- Apr 2016}\\
\emph{Teacher, Shenzhen, China}\\
\begin{itemize}
  \item Managed 15 large classes/week, developed "A for the Day" grading 
        system—drastically improved student engagement.
  \item Gained professional-level Mandarin Chinese, refining cross-cultural 
        communication and leadership in a high-intensity environment.
\end{itemize}

%==========================
% EARLY EXPERIENCE
%==========================
\resheading{Early Experience}
\textbf{University of Notre Dame Phone Center} \hfill \textit{Sep 2009 -- Jul 2012}\\
\emph{Caller}\\
\begin{itemize}
  \item Raised \$100K+ across 5 semesters by cultivating strong alumni 
        relationships and demonstrating persuasive negotiation skills.
\end{itemize}

\textbf{XR Trading} \hfill \textit{Aug 2011 -- Jan 2012}\\
\emph{IT Intern, Chicago, IL}\\
\begin{itemize}
  \item Installed, configured, and troubleshot computer hardware, software, and 
        networks for a high-frequency trading firm, honing rapid problem-solving 
        under mission-critical conditions.
\end{itemize}

%==========================
% KEY SKILLS & LANGUAGES
%==========================
\resheading{Key Skills \& Languages}
\begin{itemize}
  \item \textbf{Programming Languages}: Ruby, Javascript
  \item \textbf{Frameworks}: Rails, Stimulus
  \item \textbf{Methodologies}: Agile, Scrum, End-to-End Product Development
  \item \textbf{Spoken Languages}: English (Native), Chinese (Professional), German (Limited), Spanish (Elementary)
  \item \textbf{Additional Highlights}: Nerdery Texas Hold'em Champion (2019, 2018)
\end{itemize}

%==========================
% END DOCUMENT
%==========================
\end{document}
